Tensor denoising and completion based on ordinal observations

### 2020-02-15 ICML/arxiv/ordinalT_arxiv_v3.tex
Add files via upload

Table~\ref{table:clustering} shows the eight clusters and their compositions. We find that most brain nodes fall into cluster I and the cluster II, which can be represented as the left and right hemispheres, respectively (Figure~\ref{figure:brain image}). Clusters III-VIII captures brain regions with same annotations. For example, clusters III/IV represents the supramarginal gyrus region on the left/right hemisphere, respectively. This region is known to be involved in visual word recognition and reading~\citep{stoeckel2009supramarginal}. The results demonstrate that our clustering successfully groups similar brain regions together without knowledge of external annotation.

@@

\begin{figure}[H]
  \centering
 \includegraphics[width = 0.45\textwidth]{braincluster.pdf}
 \includegraphics[width = 0.45\textwidth]{braincluster3.pdf}
  \caption{Top two clusters of brain nodes. (a) Nodes in yellow are from cluster I (left hemisphere), and nodes in green are from cluster II (right hemisphere). (b) Predicted connectivity within cluster I/II. Edges are colored based on predicted strength level averaged across individuals.}  \label{figure:brain image}
\end{figure}

>>>>

Table~\ref{table:clustering} shows the eight clusters and their compositions. We find that most brain nodes fall into cluster I and the cluster II, which can be represented as the left and right hemispheres, respectively (Figure~\ref{figure:brain image} a,b). Clusters III-VIII capture brain regions with same annotations. For example, clusters III/IV represents the supramarginal gyrus region on the left/right hemisphere, respectively. This region is known to be involved in visual word recognition and reading~\citep{stoeckel2009supramarginal}. We increase the number of clusters to 11 and 13. When the number of clusters is 11, there are three main clusters which most of brain nodes fall into (Figure~\ref{figure:brain image} c,d). Two of them are represented as the left and right hemispheres like the previous cluster result. The other main cluster is newly captured and located in the bottom-middle part of the brain. Other small clusters are more or less the same as the small clusters in the result when the number of cluster is eight. When the number of clusters is 13, we find the four biggest clusters. We can characterize those clusters as top-left, bottom-left, top-right and bottom-right hemispheres (Figure~\ref{figure:brain image} e,f). Other clusters remain almost the same as the small clusters in the previous results, which share same annotations in each cluster.
The results demonstrate that our clustering successfully groups similar brain regions together without knowledge of external annotation.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width = 0.45\textwidth]{clustnode8.pdf}
  \includegraphics[width = 0.45\textwidth]{clustedge8.pdf}
  \includegraphics[width = 0.45\textwidth]{clustnode11.pdf}
  \includegraphics[width = 0.45\textwidth]{clustedge11.pdf}
  \includegraphics[width = 0.45\textwidth]{clustnode13.pdf}
  \includegraphics[width = 0.45\textwidth]{clustedge13.pdf}
  \caption{Cluster image of brain nodes when the number of clusters is 8 (a,b), 11 (c,d) and 13 (e,f). (a,c,e)
  Nodes from the same cluster are colored with the same color.  (b,d,f) Predicted connectivity within clusters. Edges are colored based on predicted strength level averaged across individuals.}  \label{figure:brain image}
\end{figure}
